User-level Grid Monitoring with Inca 2

### 2007-02-26 pubs/papers/hpdc-gmw-2007/paper.tex
OK shava your turn on this text... let me know when you want me to take it back.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6565 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

The GrASP probes yield useful data on the performance and reliability of the
grid infrastructure that they are run on, but in order to gather a large
amount of data over time we found it necessary to run them on a schedule and
gather any error messages that took place during the execution.  In order to
fulfill the last 2 requirements we deployed the GrASP probes as reporters
within the Inca framework.

\subsubsection{Usage of Inca}

@@

@@

Using Inca GrASP was deployed on TeraGrid and Geon for a period of over 6
months.  The data gathered during that period yielded a paper, Measuring the
Performance and Reliability of Production Computational Grids ~\cite{grasp2}.
Through the running of the GrASP probes over such an extended period of time
we were able to identify a recurring Globus 2 bug and were able to predict the
execution time of Preco, a Grid application run on the TeraGrid within 12\%
excluding setup and cleanup time.

>>>>

The GrASP probes yield useful data on the performance and reliability of the
grid infrastructure that they are run on.  In order for the data gathered to
be useful, it must gathered repeatedly over time and stored in a manner
appropriate for querying.  In addition to storing the measurements available
we also required that any error messages encountered be stored as well.    
In order to
fulfill the last 2 requirements we deployed the GrASP probes as reporters
within the Inca framework.

@@

\begin{figure*}[tbp]
  \centering
  \mbox{\epsfig{file=errorHistogramTG.eps, width=.7\textwidth}}
  \caption{\label{errorHist_fig} Histogram of Error Messages Encountered.}
\end{figure*}

@@

GrASP, using Inca, was deployed on TeraGrid and Geon for a period of over 6
months.  The data gathered during that period yielded a paper, Measuring the
Performance and Reliability of Production Computational Grids ~\cite{grasp2}.
By the running of the GrASP probes over such an extended period of time
we were able to identify a recurring Globus 2 bug.  Figure ~\ref{errorHist_fig} shows the types (shortened) and number of system errors that were detected while executing the
benchmark during the GrASP deployment on TeraGrid in 2005. The highest occurring
error was number 9, Assertion GLOBUS FALSE, which was the result of a bug in
the Globus 2 GRAM server.  We were also able to predict the
execution time of Preco, a Grid application run on the TeraGrid within 12\% (excluding setup and cleanup time).
